Cooperative Kernels: Safe Multitasking for Blocking Algorithms on GPUs

### 2016-11-10 write-ups/PLDI/paper.tex
Fixed font size.
added graph traversal example

\newcommand{\ADComment}[1]{\textcolor{green}{AD: #1}}
%\newcommand{\TSComment}[1]{\textcolor{blue}{TS: #1}}
\newcommand{\HEComment}[1]{\textcolor{orange}{HE: #1}}
%\newcommand{\COULDCUT}[1]{\textcolor{blue}{#1}}

@@

\begin{figure}
\ADComment{Tyler/Hugues: please insert graph traversal example.}
\begin{lstlisting}
TODO
\end{lstlisting}
\caption{An OpenCL graph search algorithm, using a global barrier for synchronisation}\label{fig:graphsearch}
\end{figure}

>>>>

\newcommand{\ADComment}[1]{\textcolor{green}{AD: #1}}
%\newcommand{\TSComment}[1]{\textcolor{blue}{TS: #1}}
\newcommand{\HEComment}[1]{\textcolor{orange}{HE: #1}}
%\newcommand{\COULDCUT}[1]{\textcolor{blue}{#1}}
\newcommand{\TSComment}[1]{\textcolor{purple}{TS: #1}}

@@

\begin{figure}
\ADComment{Tyler/Hugues: please insert graph traversal example.}
\TSComment{Hows this?}

\begin{lstlisting}
kernel graph_traversal(global graph *g, 
                       global nodes *n0, global nodes *n1) {

  int level = 0;
  global nodes * in_nodes = n0;
  global nodes * out_nodes = n1;

  int tid = get_global_id();
  int stride = get_global_size();

  while(in_nodes.size > 0) {

    for (int i = tid; i < nodes.size; i += stride) {
      process_node(g, in_nodes[i], out_nodes, level);
    }

    level++;
    swap(in_nodes, out_nodes);
    reset(out_nodes);
    global_barrier();
  }
}
\end{lstlisting}
\caption{An OpenCL graph traversal algorithm, using a global barrier for synchronisation}\label{fig:graphsearch}
\end{figure}
